\documentclass[10pt,twocolumn]{article}

% --- geometry + fonts ---
\usepackage[a4paper,margin=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[section]{placeins}
\usepackage[skip=6pt,font=small]{caption}
\usepackage{flushend}
\graphicspath{{../}{../figures/}}

% --- layout discipline ---
\setlength{\intextsep}{5pt plus 1pt minus 1pt}
\setlength{\textfloatsep}{6pt plus 1pt minus 1pt}
\setlength{\floatsep}{6pt plus 1pt minus 1pt}
\setlength{\dbltextfloatsep}{6pt plus 1pt minus 1pt}
\setlength{\dblfloatsep}{6pt plus 1pt minus 1pt}
\setlength{\abovecaptionskip}{3pt}
\setlength{\belowcaptionskip}{2pt}
\renewcommand{\arraystretch}{1.1}

% --- boundary-overflow protections ---
\emergencystretch=2em
\tolerance=2000
\hyphenpenalty=50
\sloppy

% --- math operators ---
\DeclareMathOperator*{\argtop}{arg\,top}

\title{Trust-Aware Context Selection: Learned Signal Combination\\for Multi-Hop Evidence Retrieval}
\author{Vikash Chandra Mishra\\[2pt]Vizuara AI Labs\\[2pt]\texttt{vikash@vizuara.com}}
\date{}

\begin{document}
\twocolumn[\begin{@twocolumnfalse}
\maketitle
\begin{abstract}
Retrieval-augmented language models increasingly depend on a pool of
heterogeneous candidate passages, and the correctness of a grounded
answer hinges on which passages enter the context window. Most
systems collapse this selection to a single relevance score, yet a
classical view of trust decomposes into several orthogonal
dimensions: relevance to the query, intrinsic authority of the
source, and corroboration across independent sources. We ask
whether combining six lightweight signals covering these three
dimensions yields better selection than any single signal, and
whether the textbook intuition for combining them is empirically
correct. On HotpotQA's distractor setting, with exactly two gold
paragraphs among ten candidates per question, we compare a naive
uniform average of three trust signals against a six-feature
logistic regression fit on only one hundred questions per seed. The
learned combiner attains Precision@2 of $0.345 \pm 0.032$, a 3.3
absolute-point improvement over the strongest single-signal baseline
SBERT at $0.312 \pm 0.035$, with the gap consistent on every seed;
the gold-versus-distractor score gap more than doubles, from $0.170$
to $0.349$, indicating substantially better calibration. The uniform
average instead collapses to $0.080$, below BM25. Inspecting the
fitted weights diagnoses why: paragraph length and cross-paragraph
consistency are learned as anti-signals, because distractors are
length-matched to gold and topically close enough that cross-source
similarity peaks among distractors rather than among the gold pair.
In distractor-rich retrieval, the classical trust heuristics are
correct in prior but wrong in sign, and supervised calibration over
a handful of examples is sufficient to recover them.
\end{abstract}
\vspace{1em}
\end{@twocolumnfalse}]

\input{introduction}

\input{related_work}

\input{method}

\input{experiments}

\input{results}

\input{conclusion}

\FloatBarrier
\bibliographystyle{unsrtnat}
\bibliography{references}

\end{document}
